Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-22 paper.qmd
Updated Figure 9

diaconis_bin_width <- calc_bins_y(
    bin1 = ceiling(NROW(training_data_scurve)^(1/3)),
    r2 = r2,
    q = 0.1)$a1

mse_scurve_b <- ggplot(error_scurve, 
                     aes(x = a1, 
                         y = MSE)) + 
  geom_point(size = 1) +
  geom_line(linewidth = 0.05) + 
  # geom_vline(xintercept = 11, linetype="solid",
  #            color = "#bdbdbd", linewidth=1) +
  geom_vline(xintercept = diaconis_bin_width, 
             linetype=2, color = "#bdbdbd", 
             linewidth=1) +
  # geom_vline(xintercept = 13, linetype=2,
  #            color = "#bdbdbd", linewidth=1) +
  #scale_x_continuous(breaks = 5:19) +
  labs(x = expression(a[1]), y = "MSE") +
  ggtitle("(a)") +
  theme(aspect.ratio = 0.75,
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12, 
            angle=90),
        axis.ticks.x = element_line(linewidth = 0.5),
        axis.ticks.y = element_line(linewidth = 0.5),
        plot.title = element_text(size = 12),
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 10),
        legend.key.height = unit(1, 'cm'),
        legend.key.width = unit(1, 'cm'),
        legend.key.size = unit(1, 'cm'))

# b1_m_scurve <- ggplot(error_scurve, 
#                      aes(x = bin1, 
#                          y = b_non_empty/b)) + 
#   geom_point(size = 1) +
#   geom_line(linewidth = 0.05) + 
#   # geom_vline(xintercept = 11, linetype="solid",
#   #            color = "#bdbdbd", linewidth=1) +
#   # geom_vline(xintercept = 9, linetype=2,
#   #            color = "#bdbdbd", linewidth=1) +
#   # geom_vline(xintercept = 13, linetype=2,
#   #            color = "#bdbdbd", linewidth=1) +
#   scale_x_continuous(breaks = 5:19) +
#   labs(x = expression(b[1]), y = expression(frac(m, b))) +
#   ggtitle("(a)") +
#   theme(aspect.ratio = 0.75,
#         axis.text.x = element_text(size = 12),
#         axis.text.y = element_text(size = 12),
#         axis.title.x = element_text(size = 12),
#         axis.title.y = element_text(size = 12, 
#             angle=90),
#         axis.ticks.x = element_line(linewidth = 0.5),
#         axis.ticks.y = element_line(linewidth = 0.5),
#         plot.title = element_text(size = 12),
#         legend.title = element_text(size = 12),
#         legend.text = element_text(size = 10),
#         legend.key.height = unit(1, 'cm'),
#         legend.key.width = unit(1, 'cm'),
#         legend.key.size = unit(1, 'cm'))
# 
# b1_m_scurve2 <- ggplot(error_scurve, 
#                      aes(x = bin1, 
#                          y = b_non_empty)) + 
#   geom_point(size = 1) +
#   geom_line(linewidth = 0.05) + 
#   # geom_vline(xintercept = 11, linetype="solid",
#   #            color = "#bdbdbd", linewidth=1) +
#   # geom_vline(xintercept = 9, linetype=2,
#   #            color = "#bdbdbd", linewidth=1) +
#   # geom_vline(xintercept = 13, linetype=2,
#   #            color = "#bdbdbd", linewidth=1) +
#   scale_x_continuous(breaks = 5:19) +
#   labs(x = expression(b[1]), y = expression(m)) +
#   ggtitle("(c)") +
#   theme(aspect.ratio = 0.75,
#         axis.text.x = element_text(size = 12),
#         axis.text.y = element_text(size = 12),
#         axis.title.x = element_text(size = 12),
#         axis.title.y = element_text(size = 12, 
#             angle=90),
#         axis.ticks.x = element_line(linewidth = 0.5),
#         axis.ticks.y = element_line(linewidth = 0.5),
#         plot.title = element_text(size = 12),
#         legend.title = element_text(size = 12),
#         legend.text = element_text(size = 10),
#         legend.key.height = unit(1, 'cm'),
#         legend.key.width = unit(1, 'cm'),
#         legend.key.size = unit(1, 'cm'))
```

@@

mse_scurve_lwd2 <- error_rm_scurve |>
  filter(b_non_empty >= 5) |>
  ggplot(aes(x = b_non_empty,y = MSE)) + 
  geom_point(
    size = 1
    ) +
  geom_line(
    linewidth = 0.3
    ) + 
  # geom_vline(xintercept = benchmark1, linetype="solid", 
  #            color = "#bdbdbd", linewidth=1, alpha = 0.5) +
  scale_x_continuous("m (b1 = 14)") + 
  ylab("MSE") +
  ggtitle("(e)") +
  theme(aspect.ratio = 0.75,
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12, 
            angle=90),
        plot.title = element_text(size = 12))
```

@@

mse_scurve_b + mse_scurve_lwd + 
  mse_scurve_lwd2 + distance_hist + 
  plot_layout(ncol=2)
```

>>>>

# diaconis_bin_width <- calc_bins_y(
#     bin1 = ceiling(NROW(training_data_scurve)^(1/3)),
#     r2 = r2,
#     q = 0.1)$a1

mse_scurve_b <- ggplot(error_scurve, 
                     aes(x = a1, 
                         y = MSE)) + 
  geom_point(size = 1) +
  geom_line(linewidth = 0.05) + 
  geom_vline(xintercept = 0.096, linetype=2,
             color = "#bdbdbd", linewidth=1) +
  geom_vline(xintercept = 0.116,
             linetype="solid",
             color = "#bdbdbd",
             linewidth=1) +
  geom_vline(xintercept = 0.184, linetype=2,
             color = "#bdbdbd", linewidth=1) +
  scale_x_continuous(breaks = sort(unique(round(error_scurve$a1, 3)))) +
  labs(x = expression(a[1]), y = "MSE") +
  ggtitle("(a)") +
  theme(aspect.ratio = 0.75,
        axis.text.x = element_text(size = 10,
                                   angle = 90),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12, 
            angle=90),
        axis.ticks.x = element_line(linewidth = 0.5),
        axis.ticks.y = element_line(linewidth = 0.5),
        plot.title = element_text(size = 12),
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 10),
        legend.key.height = unit(1, 'cm'),
        legend.key.width = unit(1, 'cm'),
        legend.key.size = unit(1, 'cm'))

a1_m_scurve <- ggplot(error_scurve,
                     aes(x = a1,
                         y = b_non_empty)) +
  geom_point(size = 1) +
  geom_line(linewidth = 0.05) +
  geom_vline(xintercept = 0.116,
           linetype=2,
           color = "#bdbdbd",
           linewidth=1) +
  geom_hline(yintercept = 52,
           linetype=2,
           color = "#bdbdbd",
           linewidth=1) +
  # geom_vline(xintercept = 11, linetype="solid",
  #            color = "#bdbdbd", linewidth=1) +
  # geom_vline(xintercept = 9, linetype=2,
  #            color = "#bdbdbd", linewidth=1) +
  # geom_vline(xintercept = 13, linetype=2,
  #            color = "#bdbdbd", linewidth=1) +
  scale_y_continuous(breaks = sort(unique(error_scurve$b_non_empty))) +
  scale_x_continuous(breaks = sort(unique(round(error_scurve$a1, 3)))) +
  labs(x = expression(a[1]), y = expression(m)) +
  ggtitle("(b)") +
  theme(aspect.ratio = 0.75,
        axis.text.x = element_text(size = 10,
                                   angle = 90),
        axis.text.y = element_text(size = 11),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12,
            angle=90),
        axis.ticks.x = element_line(linewidth = 0.5),
        axis.ticks.y = element_line(linewidth = 0.5),
        plot.title = element_text(size = 12),
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 10),
        legend.key.height = unit(1, 'cm'),
        legend.key.width = unit(1, 'cm'),
        legend.key.size = unit(1, 'cm'))
# 
# b1_m_scurve2 <- ggplot(error_scurve, 
#                      aes(x = bin1, 
#                          y = b_non_empty)) + 
#   geom_point(size = 1) +
#   geom_line(linewidth = 0.05) + 
#   # geom_vline(xintercept = 11, linetype="solid",
#   #            color = "#bdbdbd", linewidth=1) +
#   # geom_vline(xintercept = 9, linetype=2,
#   #            color = "#bdbdbd", linewidth=1) +
#   # geom_vline(xintercept = 13, linetype=2,
#   #            color = "#bdbdbd", linewidth=1) +
#   scale_x_continuous(breaks = 5:19) +
#   labs(x = expression(b[1]), y = expression(m)) +
#   ggtitle("(c)") +
#   theme(aspect.ratio = 0.75,
#         axis.text.x = element_text(size = 12),
#         axis.text.y = element_text(size = 12),
#         axis.title.x = element_text(size = 12),
#         axis.title.y = element_text(size = 12, 
#             angle=90),
#         axis.ticks.x = element_line(linewidth = 0.5),
#         axis.ticks.y = element_line(linewidth = 0.5),
#         plot.title = element_text(size = 12),
#         legend.title = element_text(size = 12),
#         legend.text = element_text(size = 10),
#         legend.key.height = unit(1, 'cm'),
#         legend.key.width = unit(1, 'cm'),
#         legend.key.size = unit(1, 'cm'))
```

@@

# mse_scurve_lwd2 <- error_rm_scurve |>
#   filter(b_non_empty >= 5) |>
#   ggplot(aes(x = b_non_empty,y = MSE)) + 
#   geom_point(
#     size = 1
#     ) +
#   geom_line(
#     linewidth = 0.3
#     ) + 
#   # geom_vline(xintercept = benchmark1, linetype="solid", 
#   #            color = "#bdbdbd", linewidth=1, alpha = 0.5) +
#   scale_x_continuous("m (b1 = 14)") + 
#   ylab("MSE") +
#   ggtitle("(e)") +
#   theme(aspect.ratio = 0.75,
#         axis.text.x = element_text(size = 12),
#         axis.text.y = element_text(size = 12),
#         axis.title.x = element_text(size = 12),
#         axis.title.y = element_text(size = 12, 
#             angle=90),
#         plot.title = element_text(size = 12))
```

@@

mse_scurve_b + a1_m_scurve +
  mse_scurve_lwd + distance_hist + 
  plot_layout(ncol=2)
```
